\Title

### 2020-01-14 manuscript/manuscript.tex
Shrink manuscript to 80 chars per line

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{A better strategy for interpolating gravity and magnetic data}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        S.R. Soler$^{1,2}$,
        L. Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$University of Liverpool} \\

}
\newcommand{\DOI}{doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}}
\newcommand{\DOILink}{\href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}}

@@

% Describe the proposed source distributions as combination of layouts and depths
% strategies.

@@

Create synthetic surveys to produce observation points.
In order to compare each source layout under very different set of observation points we
create a ground and an airborne synthetic surveys.
We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J. Kleywegt
et al.\ and made available through the NOAA website
(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating a synthetic
ground survey.
We selected a portion of the Great Britain Aeromagnetic Survey acquired by Hunting
Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955 and 1965 and made
available by the
\href{
    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
    }{
    British Geological Survey (BGS)
}, for creating a synthetic airborne survey.

@@

%Describe the target grid. Show target grid figure.
%Describe the parameters used for each source distribution, how do we score each interpolation.
%Describe the Harmonica implementation of the EQL.
%Show results.

>>>>

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{
    A better strategy for interpolating gravity and magnetic data
}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        S.R. Soler$^{1,2}$,
        L. Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$University of Liverpool} \\

}
\newcommand{\DOI}{
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

@@

% Describe the proposed source distributions as combination of layouts and
% depths strategies.

@@

Create synthetic surveys to produce observation points.
In order to compare each source layout under very different set of observation
points we create a ground and an airborne synthetic surveys.
We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J.
Kleywegt et al.\ and made available through the NOAA website
(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating
a synthetic ground survey.
We selected a portion of the Great Britain Aeromagnetic Survey acquired by
Hunting Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955
and 1965 and made available by the
\href{
    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
    }{
    British Geological Survey (BGS)
}
, for creating a synthetic airborne survey.

@@

%Describe the target grid. Show target grid figure.
%Describe the parameters used for each source distribution, how do we score
%each interpolation.
%Describe the Harmonica implementation of the EQL.
%Show results.
